Multi-EWAS enrichment example

### 2024-06-22 figs/multi_ewas_example.Rmd
cancer bioinformatics symposium

>>>>

Make a special heatmap for the cancer bioinformamtics symposium.

```{r,cancerheat}

names(r1) <- names(l2)

r3 <- r1[grep("cancer",names(r1))]

r4 <- lapply(r3,function(r) {
  r <- subset(r,p.adjustANOVA<0.05)
  ups <- head(r[order(-r$s.dist),],3)$set
  dns <- head(r[order(r$s.dist),],3)$set
  list("ups"=ups,"dns"=dns)
} )

r4

gsets <- unique(unname(unlist(r4)))
gsets

top <- mtable2[which(mtable2$set %in% gsets),]
top <- top[,c(1,4:22)]
top <- top[,colnames(top) %in% c("set","s.breast_cancer","s.colorectal_can","s.lung_cancer","s.ovarian_cancer","s.prostate_cance")]

rownames(top) <- top$set
top$set=NULL
head(top,3)

rownames(top) <- gsub("REACTOME_","",rownames(top))
rownames(top) <- gsub("_"," ",rownames(top))

colnames(top) <- c("breast","colorectal","lung","ovarian","prostate")
head(top)

saveRDS(top,file="cancerheat.Rds")

heatmap.2(as.matrix(top),scale="none",trace="none",margins=c(10,25),
  col=colfunc(25),cexRow=0.75,cexCol=1.2)

pdf("cancerheat.pdf",height=7,width=7)
heatmap.2(as.matrix(top),scale="none",trace="none",margins=c(10,25),
  col=colfunc(25),cexRow=0.7,cexCol=1.2)
dev.off()
